Flavour Symmetry Embedded - GLoBES (FaSE-GLoBES)

### 2020-05-26 doc/paper.tex
update docs

{\color{blue}There are three methods to translate from $\vec{\theta}_{Model}$ to $\vec{\theta}_{OSC}$ in \textbf{FaSE-GLoBES}:} the user can assign the correlation between the standard oscillation and model parameter sets{\color{blue}, give the mixing matrix in model parameter $U$}, or define the mass matrix in model parameters, which will be diagonalised by the function \texttt{STAN\_OSC} to obtain the corresponding oscillation-parameter values. 
%The relation between the oscillation and model parameter sets can be derived out by the user, 
In the way of directly giving the relation between oscillation and model parameter sets, the user needs to provide
{\color{blue}
\begin{equation}
\vec{\theta}_{Model}=\vec{f}(\vec{\theta}_{OSC}), 
\end{equation}
in the function \texttt{MtoS}. }
%

>>>>

{\color{blue}There are three methods to translate from $\vec{\theta}_{Model}$ to $\vec{\theta}_{OSC}$ in \textbf{FaSE-GLoBES}:} 1).~the user can assign the correlation between the standard oscillation and model parameter sets{\color{blue}, 2).~give the mixing matrix in model parameter $U$}, or 3).~define the mass matrix in model parameters. 
%The relation between the oscillation and model parameter sets can be derived out by the user, 
In the way of directly giving the relation between oscillation and model parameter sets, the user needs to provide
{\color{blue}
\begin{equation}
\vec{\theta}_{Model}=\vec{f}(\vec{\theta}_{OSC}), 
\end{equation}
in the function \texttt{MtoS}. }
%
